Comparing LUCA runs for station all

### 2024-08-19 compare_luca_runs.Rmd
updating luca comparisons

kge <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs/kge_compare.csv')

@@

# Parameters

@@

statn_all1 <- read_cals(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals(statn_all12, name = 'statn_all12')

statn <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  # mutate(input_data = 'grid') %>%
  # mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  # mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  # dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

#function to plot all params
plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = cal,
               y = value)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plot_params)
```

@@

@@

statn_all1 <- read_cals_burn(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals_burn(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals_burn(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals_burn(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals_burn(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals_burn(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals_burn(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals_burn(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals_burn(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals_burn(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals_burn(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals_burn(statn_all12, name = 'statn_all12')

burn_params <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  filter(soilID == 22) %>%
  dplyr::select(-soilID) %>% 
  pivot_longer(!cal, 
               names_to = 'params',
               values_to = 'value') %>% 
  mutate(params = str_remove(params, 'luca_')) %>%
  mutate(params = as.factor(params),
         burn = 'yes')

@@

@@

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

lapply(name2, plot_burnparams)
```

@@

>>>>

kge <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs/kge_compare.csv') %>%
  filter(!cal == 'statn_all1')

@@

# Unburned parameters

@@

#statn_all1 <- read_cals(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals(statn_all12, name = 'statn_all12')

statn <- bind_rows(#statn_all1, 
                   statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  # mutate(input_data = 'grid') %>%
  # mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  # mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  # dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

limits <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/param_limits.csv')

params_limits <- left_join(params, limits, by = 'param') %>%
  mutate(param = as.factor(param))

#function to plot all params
plot_params <- function(param_name) {
  params_limits %>%
    filter(param == param_name) %>%
    ggplot(aes(x = cal,
               y = value)) + 
    geom_hline(aes(yintercept = lower), color = 'red') +
    geom_hline(aes(yintercept = upper), color = 'red') + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params_limits$param)

@@

## Metrics

params_summary <- params %>%
  group_by(param) %>%
  summarize(mean = mean(value),
            sd = sd(value),
            cv = sd(value)/mean(value),
            min = min(value),
            max = max(value))

kable(params_summary, digits = 2) %>%
  kable_styling(full_width = F)

@@

#statn_all1 <- read_cals_burn(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals_burn(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals_burn(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals_burn(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals_burn(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals_burn(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals_burn(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals_burn(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals_burn(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals_burn(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals_burn(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals_burn(statn_all12, name = 'statn_all12')

burn_params <- bind_rows(#statn_all1, 
                         statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  filter(soilID == 22) %>%
  dplyr::select(-soilID) %>% 
  pivot_longer(!cal, 
               names_to = 'params',
               values_to = 'value') %>% 
  mutate(params = str_remove(params, 'luca_')) %>%
  mutate(params = as.factor(params),
         burn = 'yes')

@@

# Burned parameters

@@

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}

burn_limits <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/burn_param_limits.csv')

burn_params_limits <- left_join(burn_params, burn_limits, by = 'params') %>%
  mutate(params = as.factor(params))

plot_burnparams <- function(param_name) {
  burn_params_limits %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal)) +
    geom_hline(aes(yintercept = lower), color = 'red') +
    geom_hline(aes(yintercept = upper), color = 'red') + 
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

name2 <- levels(burn_params_limits$params)

@@

## Burned metrics

burn_params_summary <- burn_params %>%
  group_by(params) %>%
  summarize(mean = mean(value),
            sd = sd(value),
            cv = sd(value)/mean(value),
            min = min(value),
            max = max(value))

kable(burn_params_summary, digits = 2) %>%
  kable_styling(full_width = F)
